---
title: "Attitudes Towards Gender Roles and Immigration"
author: "Sungjoo Cho"
date: "`r Sys.Date()`"
output: html_document
params:
   nms: Austria
---

```{r include=FALSE}
# library
library(dplyr)
library(tidyr)
library(haven)
library(knitr)
library(ggplot2)
library(summarytools)
library(ggExtra)
library(texreg)
library(plotly)
library(sjlabelled)
library(tidyverse)
library(broom)
```


```{r, include=FALSE}
## run dynamic report

# load cleaned data
evs <- readRDS("data/evs.rds")

# iteration function for batch creation
render_report <- function(path, cntry) {
  rmarkdown::render(
    path,
    params = list(nms = cntry),
    output_file = paste0("reports/evs_report-", cntry, ".html"))}

analysis_evs <- evs[evs$cntry == params$nms, ]

# iterate over each unique country name and render report
map(unique(evs$cntry),
    render_report,
    path = "dynamic_reports.Rmd")
```


## Report on `r params$nms`

### Introduction

This report explores attitudes towards gender roles and immigration in `r params$nms` using data from [2017 European Value Study (EVS)](https://search.gesis.org/research_data/ZA7500). Key variables analyzed include v72 and v80, which respectively measure perceptions on maternal employment effects and job priority during scarcity. We will incorporates demographic information such as age, sex, and education level for a comprehensive analyses. 

-   **v72** - Child suffers with working mother
    -   Question: When a mother works for pay, the children suffer
    -   Scale: 1 (Strongly agree) to 4 (Strongly disagree)
-   **v80** - Jobs are scarce:giving...(nation)priority
    -   Question: When jobs are scarce, employers should give priority to [Nationality] people over immigrants"
    -   Scale: 1 (Strongly agree) to 4 (Strongly disagree)


### Descriptive Analysis

Below tables are descriptive statistics for both continuous (v72, v80, age) and categorical variables (sex, education) in `r params$nms`.

```{r echo=FALSE}
# table for continuous variables
sum_v72 <- summary(analysis_evs$v72)
sum_v80 <- summary(analysis_evs$v80)
sum_age <- summary(analysis_evs$age)

tab_continuous <- tibble("Variables" = c("v72", "v80", "age"),
                         "Mininum" = c(sum_v72["Min."], sum_v80["Min."], sum_age["Min."]),
                         "1st Qu." = c(sum_v72["1st Qu."], sum_v80["1st Qu."], sum_age["1st Qu."]),
                         "Median" = c(sum_v72["Median"], sum_v80["Median"], sum_age["Median"]),
                         "Mean" = c(round(sum_v72["Mean"], 3), round(sum_v80["Mean"], 3), sum_age["Mean"]),
                         "3rd Qu." = c(sum_v72["3rd Qu."], sum_v80["3rd Qu."], sum_age["3rd Qu."]),
                         "Maximum" = c(sum_v72["Max."], sum_v80["Max."], sum_age["Max."]))

kable(tab_continuous, caption = "Summary Statistics for v72 and v80")
```

```{r echo=FALSE}
# table for categorical variables
analysis_evs$sex <- factor(analysis_evs$sex, levels = c(1, 2), labels = c("Male", "Female"))
analysis_evs$edu <- factor(analysis_evs$edu, levels = c(1, 2, 3, 66), labels = c("lower", "medium", "higher", "other"))

analysis_evs_sex <- analysis_evs %>%
  group_by(sex) %>%
  summarise(frequency = n(),
            proportion = round(n()/nrow(evs), 4)) %>%
  mutate(variable = "sex",
         value = sex) %>%
  select(variable, value, frequency, proportion)

analysis_evs_edu <- analysis_evs %>%
  group_by(edu) %>%
  summarise(frequency = n(),
            proportion = round(n()/nrow(analysis_evs), 4)) %>%
  mutate(variable = "education",
         value = edu) %>%
  select(variable, value, frequency, proportion)

tab_categorical <- bind_rows(analysis_evs_sex, analysis_evs_edu)
kable(tab_categorical, caption = "Summary Statistics for sex and education")
```

### Change in Attitudes by Age

The two graphs presented below illustrates how the two variables of interest change with age in `r params$nms`. The X-axis denotes age, while the Y-axis represents the average level of disagreement for v72 and v80.

```{r echo=FALSE}
# table of average v72 and v80 by age
tab_ave_age <- analysis_evs %>%
  select(v72, v80, age) %>%
  group_by(age) %>%
  summarise(v72 = mean(v72, na.rm = TRUE),
            v80 = mean(v80, na.rm = TRUE))

# grraph for v72
chart_ave_v72 <- ggplot(tab_ave_age, aes(x=age, y=v72)) +
  geom_line(color = "blue") +
              labs(title = "Average Disagreement of v72 by Age", 
                   x = "Age", 
                   y = "Average Disagreement")

ggplotly(chart_ave_v72)


  # grraph for v80
chart_ave_v80 <- ggplot(tab_ave_age, aes(x=age, y=v80)) +
  geom_line(color = "blue") +
              labs(title = "Average Disagreement of v80 by Age", 
                   x = "Age", 
                   y = "Average Disagreement")
ggplotly(chart_ave_v80)
```


### Regression models

The table below shows regression models for both attitudes towards Child suffers (v72) and Job to national (v80) in `r params$nms`. The models include respondents' age, age squared, sex and education.

```{r echo=FALSE, results='asis'}
analysis_evs$edu <- as.factor(analysis_evs$edu)
analysis_evs$sex <- as.factor(analysis_evs$sex)

# regression model of v72
reg_v72 <- lm(v72 ~ age + I(age^2) + sex + edu, data = analysis_evs)

# regression model of v80
reg_v80 <- lm(v80 ~ age + I(age^2) + sex + edu, data = analysis_evs)

# present outputs from stats model texreg (texreg: pdf, htmlreg: html)
model_names <- c("Child suffers(v72)", "Job to national(v80)")

htmlreg(list(reg_v72, reg_v80), 
        custom.model.names = model_names,
        caption = "Outputs from Regression Models", type = "html")
```

```{r echo=FALSE}
# model interpretation (v72)
interpret_72 <- function(model) {
  
  coeffs <- coef(summary(model))
  p_values <- coeffs["sexFemale", "Pr(>|t|)"]
  estimates <- coeffs["sexFemale", "Estimate"]
  
  if(p_values < 0.05) {
    if(estimates > 0) {
    interpretation <- paste("Based on the model above, it appears that the sex variable has a significant impact on v72. It shows that females are more likely to disagree that the child suffers if the mother works by", round(estimates, 2), "compared to males, showing a positive relationship. (p<0.05)")
  } else if (estimates < 0) {
    interpretation <- paste("Based on the model above, it appears that the sex variable has a significant impact on v72. It shows that females are less likely to disagree that the child suffers if the mother works by", round(estimates, 2), "compared to males, showing a negative relationship (p<0.05).")
  } else {
    interpretation <- "Based on the model above, it appears that the sex variable has a statistically significant relationship with the dependent variable (p<0.05)."
  }
} else {
  interpretation <- "Based on the model above, it appears that the sex variable is not statistically significant on attitudes towards child suffer (p>0.05)."
}
  return(interpretation)
}
```


```{r echo=FALSE}
# model interpretation (v72)
interpret_80 <- function(model) {
  
  coeffs <- coef(summary(model))
  p_values <- coeffs["sexFemale", "Pr(>|t|)"]
  estimates <- coeffs["sexFemale", "Estimate"]
  
  if(p_values < 0.05) {
    if(estimates > 0) {
    interpretation <- paste("In the Job to national(v80) model, it appears that the sex variable has a significant impact on v80. It shows that females are more likely to disagree that a national should have priority for jobs when these are scarce by around ", round(estimates, 2), "compared to males, showing a positive relationship. (p<0.05)")
  } else if (estimates < 0) {
    interpretation <- paste("In the Job to national(v80) model, it appears that the sex variable has a significant impact on v80. It shows that females are less likely to disagree that a national should have priority for jobs when these are scarce by around", round(estimates, 2), "compared to males, showing a negative relationship (p<0.05).")
  } else {
    interpretation <- "In the Job to national(v80) model, it appears that the sex variable has a statistically significant relationship with the dependent variable (p<0.05)."
  }
} else {
  interpretation <- "In the Job to national(v80) model, it appears that the sex variable is not statistically significant on attitudes national (p>0.05)."
}
  return(interpretation)
}
```

`r interpret_72(reg_v72)`
`r interpret_80(reg_v80)`



